\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
\usepackage[top=4cm, bottom=4cm, left=2cm, right=2cm]{geometry}

\title{\textbf{Projet d'Algorithmique Réparti Avancé}}
\author{Coriat Florent et Pitton Olivier}
\date{29 octobre 2013}

\begin{document}
\maketitle
\newpage

\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 1} \textit{Draw a picture showing a Z-configuration on a square O6Grid of side 7. By convenience, design your picture using a grid representation (see for instance Figures 2 and 3).}
\end{minipage}}
\paragraph{}

% Answer here

\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 2} \textit{Give an algorithm for Phase Tower.}
\end{minipage}}
\paragraph{}

% Answer here

\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 3} \textit{Prove that the algorithm provided in Question 2 creates a tower with probability 1.}
\end{minipage}}
\paragraph{}

% Answer here

\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 4} \textit{Given a node u, if atu < btu and (atu diff btu diff S/2), then there exists an orientation of O-Grid such that u = (atu, btu).}
\end{minipage}}
\paragraph{}

% Answer here


\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 5} \textit{Give a formal algorithm performing Phase 1.}
\end{minipage}}
\paragraph{}

% Answer here


\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 6} \textit{Show that the three above conditions together require S >= 7.}
\end{minipage}}
\paragraph{}

% Answer here


\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 7} \textit{Similarly as in Figure 3, sketch the behavior of Phase 2 in an O-Grid. Choose S = 15.}
\end{minipage}}
\paragraph{}

% Answer here

\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 8} \textit{Try to provider either a formal algorithm or a sketch of Phase Setup. Include explanations.}
\end{minipage}}
\paragraph{}

% Answer here


\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 9} \textit{Do you think that it could be possible to achieve a deterministic algorithm with only 4 robots ?
             If yes, then sketch your algorithm. If not, what about 5 robots ?}
\end{minipage}}
\paragraph{}

% Answer here


\paragraph{}
\fbox{\begin{minipage}{1\textwidth}\textbf{Question 10} \textit{Would it be possible to achieve a probabilistic or deterministic algorithm with 3 robots ?}
\end{minipage}}
\paragraph{}

% Answer here

\end{document}
